Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-28 paper/compilation.tex
adding some references

Before checking if policies captured by the PGIR are safe, we minimize the PGIR to improve our safety analysis. 
The minimization is based on the observation that, although every path in the PGIR is a valid path in the topology, we do not want to consider paths that form loops. In particular, BGP's loop prevention mechanism forces an AS to reject any route for which it is already in the AS path.
%
For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid topological path, leading to a path that satisfies the preference 1 policy, but which contains a loop.
%
It often simplifies the failure-safety analysis to eliminate cases that are not possible due to loops. 
%For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
We use graph dominators~\ref{bib:todo} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading to $y$ from the start node. Many efficient algorithms exist for finding graph dominators in practice~\ref{bib:todo}.
%We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node. 
For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it must go through another $W$ in either case.
Colored nodes and dashed edges are removed after minimization since they are irrelvant to the BGP decision process.
%
%Although fully minimizing this graph is an NP-complete problem,  a simple and efficient algorithm based on graph dominators achieves largely the same effect, greatly simplifying the failure safety analysis.

>>>>

Before checking if policies captured by the PGIR are safe, we minimize the PGIR to improve our safety analysis. 
The minimization is based on the observation that, although every path in the PGIR is a valid path in the topology, we do not want to consider paths that form loops. In particular, BGP's loop prevention mechanism forces an AS to reject any route for which it is already in the AS path.
%
For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid topological path, leading to a path that satisfies the preference 1 policy, but which contains a loop.
%
It often simplifies the failure-safety analysis to eliminate cases that are not possible due to loops. 
%For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
We use graph dominators~\cite{tarjan-dominance} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading to $y$ from the start node. Many efficient algorithms exist for finding graph dominators in practice~\cite{linear-dominance, fast-dominance, tarjan-dominance}.
%We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node. 
For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it must go through another $W$ in either case.
Colored nodes and dashed edges are removed after minimization since they are irrelvant to the BGP decision process.
%
%Although fully minimizing this graph is an NP-complete problem,  a simple and efficient algorithm based on graph dominators achieves largely the same effect, greatly simplifying the failure safety analysis.

### 2016-01-28 paper/implementation.tex
adding some references

Constructing automata for extended regular expressions (regular expressions including negation and intersection) are known to have high complexity~\ref{bib:todo}. The \sysname compiler uses regular expressions derivatives~\ref{bib:todo} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently. Since regular expressions are defined over a finite alphabet, and since much of the AS topology is unknown, we set the alphabet to include all uniquely referenced external ASes in the policy. Similarly, to model the unknown external AS topology beyond immediate peers, we include a special topology node to represent any unknown location.
%
Rather than construct the product graph in full, our implementation prevents exploring parts of the graph when no accepting state is reachable in any of the corresponding regular automata during construction.

@@

The \sysname compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\ref{bib:todo}. More complex algorithms with better theoretical complexity exist~\ref{bib:todo} and may be better suited for large enough topologies. All minimization steps are repeated until no more progress can be made.

>>>>

Constructing automata for extended regular expressions (regular expressions including negation and intersection) are known to have high complexity~\ref{bib:todo}. The \sysname compiler uses regular expressions derivatives~\cite{regex-derivatives} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently. Since regular expressions are defined over a finite alphabet, and since much of the AS topology is unknown, we set the alphabet to include all uniquely referenced external ASes in the policy. Similarly, to model the unknown external AS topology beyond immediate peers, we include a special topology node to represent any unknown location.
%
Rather than construct the product graph in full, our implementation prevents exploring parts of the graph when no accepting state is reachable in any of the corresponding regular automata during construction.

@@

The \sysname compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\cite{fast-dominance}. More complex algorithms with better theoretical complexity exist~\cite{linear-dominance, tarjan-dominance} and may be better suited for large enough topologies. All minimization steps are repeated until no more progress can be made.
